Dataset table

### 2017-12-20 analyses/04-table-datasets.Rmd
Minor tidying of code
Remove extinctions for Brusatte and Bapst data

## Mass extinction
mass <- c("66 (K-Pg)", "66 (K-Pg)", "66 (K-Pg)", "443 (O-S)")

@@

## Table caption
table_caption <- "Details of the datasets used in this study."

@@

## Time subsets table

>>>>

## Mass extinction
mass <- c("66 (K-Pg)", "NA", "NA", "443 (O-S)")

@@

## Table caption
table_caption <- "Details of the datasets used in this study. Note that although Brusatte2014 and Bapst2016 cross the Cretaceaous Palaeogene (K-Pg) mass extinction there are not enough taxa post K-Pg to investigate the effects of the mass extinction on disparity."

@@

This produces a nicely formatted LaTeX table. Some edits will need to be made before it is incorporated into a document but it contains all the basic information required.
